A Comparative study of Dask and Spark for data-intensive neuroimaging pipelines

### 2019-07-16 latex/paper.tex
typos

%%% BIDS EXAMPLE %%%
\subsection{BidsApp example: Number of workers}
Figure~\ref{fig:bids_ms_worker} shows the makespan of the application while varying
the amount of worker. Overall, there is no substantial difference between the
engines however Futures are always slightly faster. The performance difference between
Futures and the other APIs increase with the number of workers. The makespan scales
well with the increase in workers however the scaling reduces considerably when
reaching 8 workers. This due to the IO requirement increasing with the number of
workers, since more tasks are read concurrently, and the application becomes more data
intensive.

>>>>

%%% BIDS EXAMPLE %%%
\subsection{BidsApp example: Number of workers}
Figure~\ref{fig:bids_ms_worker} shows the makespan of the application while varying
the amount of worker. Overall, there is no substantial difference between the
engines however Futures are always slightly faster. The performance difference between
Futures and the other APIs increases with the number of workers. The makespan scales
well with the increase in workers however the scaling reduces considerably when
reaching 8 workers. This is due to the IO requirement increasing with the number of
workers, since more tasks are read concurrently, and the application becomes more
data-intensive.
